Figures from: Vertebrate host availability and the thermal properties of mosquito-borne parasite transmission

### 2023-05-26 manuscript-figures.Rmd
Update manuscript-figures.Rmd

<!-- ```{r table-2_Toptdiffbound, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Toptdiffbound} Calculating how large the difference between the Ross-Macdonald and Chitnis Topt estimates can be.'} -->

<!-- # Estimating the difference between Topt and Topt_RM numerically using our previous data -->
<!-- Toptdiff_df1 <- ThermPathChars %>% -->
<!--   select(system_ID, sigmaH, KH, Topt) %>% -->
<!--   filter(is.finite(sigmaH)) %>% -->
<!--   distinct() -->

<!-- Toptdiff_df2 <- ThermPathChars %>% -->
<!--   filter(is.infinite(sigmaH)) %>% -->
<!--   select(system_ID, KH, Topt) %>% -->
<!--   rename(Topt_RM = Topt) %>% -->
<!--   distinct() -->

<!-- Toptdiff_df <- left_join(Toptdiff_df1, Toptdiff_df2) %>% -->
<!--   mutate(Toptdiff = Topt_RM - Topt) %>% -->
<!--   mutate(absToptdiff = abs(Toptdiff)) %>% -->
<!--   mutate(propToptdiff = (Topt_RM - Topt) / Topt_RM) %>% -->
<!--   mutate(sigmaHKH = sigmaH * KH) %>% -->
<!--   group_by(system_ID) %>% -->
<!--   filter(absToptdiff == max(absToptdiff)) %>% -->
<!--   select(-sigmaH, -KH, -sigmaHKH, -absToptdiff) %>% -->
<!--   distinct() -->

<!-- # Calculating Topt0 using the "simplified" equation -->
<!-- Topt0_df <- VecParms %>% -->
<!--   mutate(P_EIP = exp(-muV / etaV)) %>% -->
<!--   mutate(proxy_0 = betaV * P_EIP / (muV * V0)) %>% -->
<!--   filter(is.finite(proxy_0)) %>% -->
<!--   select(system_ID, Temperature, proxy_0) %>% -->
<!--   group_by(system_ID) -->

<!-- Topt0_base_estimates <- Topt0_df %>% -->
<!--   group_by(system_ID) %>% -->
<!--   # Calculate Topt_0 -->
<!--   filter(proxy_0 == proxy_0[which.max(proxy_0)]) %>% -->
<!--   rename(Topt_0 = Temperature) -->
<!-- # check with above: Topt_0 matches with Topt when sigmaH*KH is minimized -->
<!-- # also shows that these estimates are independent of KL (and thus ABSOLUTE adult mosquito density) -->

<!-- # Calculating Topt0 using the "simplified" equation -->
<!-- ToptRM_df <- VecParms %>% -->
<!--   mutate(P_EIP = exp(-muV / etaV)) %>% -->
<!--   mutate(proxy_RM = sigmaV^2 * V0 * betaV * P_EIP / muV) %>% -->
<!--   select(system_ID, Temperature, proxy_RM) %>% -->
<!--   group_by(system_ID) -->

<!-- ToptRM_base_estimates <- ToptRM_df %>% -->
<!--   group_by(system_ID) %>% -->
<!--   # Calculate Topt_RM -->
<!--   filter(proxy_RM == proxy_RM[which.max(proxy_RM)]) %>% -->
<!--   rename(Topt_RM = Temperature) -->
<!-- # check with above: Topt_RM matches with Topt when sigmaH*KH is maximized -->
<!-- # also shows that these estimates are independent of KL (and thus ABSOLUTE adult mosquito density) -->

<!-- Topt_estimates <- left_join(ToptRM_base_estimates, Topt0_base_estimates) %>% -->
<!--   select(system_ID, Topt_RM, Topt_0) %>% -->
<!--   mutate(Topt_diff = Topt_RM - Topt_0) %>% -->
<!--   mutate(prop_Topt_diff = abs(Topt_diff) / Topt_RM) -->

<!-- # Investigating Topt_RM and Topt_0 further -->

<!-- test_df <- VecParms %>% -->
<!--   mutate(P_EIP = exp(-muV / etaV)) %>% -->
<!--   mutate(sigmaVV0 = sigmaV * V0) %>% -->
<!--   mutate(proxy_0 = betaV * P_EIP / (muV * V0)) %>% -->
<!--   mutate(proxy_RM = sigmaV^2 * V0 * betaV * P_EIP / muV) %>% # = sigmaVV0^2*proxy_0 -->
<!--   filter(is.finite(proxy_0)) %>% -->
<!--   select(system_ID, Temperature, proxy_RM, proxy_0, sigmaVV0) -->
<!-- ``` -->

>>>>

```{r table-2_Toptdiffbound, dev = c('pdf','svg', 'png'), message=FALSE, out.width='100%', fig.width=9, fig.height=6, fig.align='center', fig.cap='\\label{fig:Toptdiffbound} Calculating how large the difference between the Ross-Macdonald and Chitnis Topt estimates can be.'}

# Estimating the difference between Topt and Topt_RM numerically using our previous data
Toptdiff_CCH <- data.Topt %>%
  ungroup() %>% 
  select(system_ID, sigmaH, KH, median) %>%
  rename(Topt = median) %>%
  filter(is.finite(sigmaH)) %>%
  distinct()

Toptdiff_RM <- data.Topt %>%
  ungroup() %>% 
  filter(is.infinite(sigmaH)) %>%
  select(system_ID, KH, median) %>%
  rename(Topt_RM = median) %>%
  distinct()

Toptdiff_df <- left_join(Toptdiff_CCH, Toptdiff_RM) %>%
  mutate(Toptdiff = Topt_RM - Topt) %>%
  mutate(absToptdiff = abs(Toptdiff)) %>%
  mutate(propToptdiff = (Topt_RM - Topt) / Topt_RM) %>%
  mutate(sigmaHKH = sigmaH * KH) %>%
  group_by(system_ID) %>%
  filter(absToptdiff == max(absToptdiff)) %>%
  select(-sigmaH, -KH, -sigmaHKH, -absToptdiff) %>%
  distinct()

# Calculating Topt0 using the "simplified" equation
Topt0_df <- median.Vec %>%
  filter(V0 > 1) %>% 
  mutate(muV = 1/(lf + eps)) %>% 
  mutate(P_EIP = exp(-muV / etaV)) %>%
  mutate(proxy_0 = lf * betaV * P_EIP / (KL * rhoL * (lf - 1 / (sigmaV_f * deltaL)))) %>%
  select(system_ID, Temperature, proxy_0) %>%
  group_by(system_ID)

test_plot <- Topt0_df %>% 
  ggplot(aes(x = Temperature, y = proxy_0)) +
  geom_point() +
  facet_wrap(~system_ID, scales = "free")
test_plot

Topt0_base_estimates <- Topt0_df %>%
  group_by(system_ID) %>%
  # Calculate Topt_0
  filter(proxy_0 == proxy_0[which.max(proxy_0)]) %>%
  rename(Topt_0 = Temperature)
# check with above: Topt_0 matches with Topt when sigmaH*KH is minimized
# also shows that these estimates are independent of KL (and thus ABSOLUTE adult mosquito density)

# Calculating Topt0 using the "simplified" equation
ToptRM_df <- median.Vec %>%
  mutate(muV = 1/(lf + eps)) %>% 
  mutate(P_EIP = exp(-muV / etaV)) %>%
  mutate(proxy_RM = sigmaV^2 * V0 * betaV * P_EIP / muV) %>%
  select(system_ID, Temperature, proxy_RM) %>%
  group_by(system_ID)

ToptRM_base_estimates <- data.Topt %>%
  group_by(system_ID) %>%
  filter(is.infinite(sigmaH)) %>% 
  select(system_ID, median) %>% 
  rename(Topt_RM = median) %>% 
  distinct()
  # Calculate Topt_RM
  # filter(proxy_RM == proxy_RM[which.max(proxy_RM)]) %>%
  # rename(Topt_RM = Temperature)
# check with above: Topt_RM matches with Topt when sigmaH*KH is maximized
# also shows that these estimates are independent of KL (and thus ABSOLUTE adult mosquito density)

Topt_estimates_median <- left_join(ToptRM_base_estimates, Topt0_base_estimates) %>%
  select(system_ID, Topt_RM, Topt_0) %>%
  mutate(Topt_diff = Topt_RM - Topt_0) %>%
  mutate(prop_Topt_diff = abs(Topt_diff) / Topt_RM)

# Investigating Topt_RM and Topt_0 further

test_df <- median.Vec %>%
  mutate(muV = 1/(lf + eps)) %>% 
  mutate(P_EIP = exp(-muV / etaV)) %>%
  mutate(sigmaVV0 = sigmaV * V0) %>%
  mutate(proxy_0 = betaV * P_EIP / (muV * V0)) %>%
  mutate(proxy_RM = sigmaV^2 * V0 * betaV * P_EIP / muV) %>% # = sigmaVV0^2*proxy_0
  filter(is.finite(proxy_0)) %>%
  select(system_ID, Temperature, proxy_RM, proxy_0, sigmaVV0)
```
